% !TEX root = SystemTemplate.tex
\chapter{Design  and Implementation}
This section will describe the design details for each of the major components 
in the system. 
 

\section{Parse Directory Function}

\subsection{Technologies  Used}
C++, Linux.

\subsection{Component  Overview}
This function will look for a C++ file, once it finds a C++ file it will compile it. 
This function will then call the find test, and run difference functions to run a test
and to see if there is a difference between the actual and expected outputs.

\subsection{Phase Overview}
This can traverse a directory, it can find and compile source code. It can look for, find, 
and run test cases. It can check for differences, and write to a log file.



\section{Find Test Function}

\subsection{Technologies  Used}
This will use C++ and system call function

\subsection{Component  Overview}
This function will travese a directory to find, and run test cases in our compiled 
source code. It will also write if the test case passed or failed, and increment our 
total count of passed and failed for the end of the log file.

\subsection{Phase Overview}
This function can traverse a directory looking for test case.  It can also run those 
test cases when it finds them, and write the results to the log file.  It also increments
the counter. 


\section{Run Difference Function}

\subsection{Technologies  Used}
This uses the C++, and system call function, as well as the diff function in Linux/GNU

\subsection{Component  Overview}
This function will create a function that will run the diff function in Linux/GNU via the system call.
First however it must create the string that will invoke the call, and take in the file names. Then it 
will pass inform others if the test case passed or failed so they can handle the information accourdingly. 
Also this doesn't print anything to the screen if there is a difference between the two files.

\subsection{Phase Overview}
This function can create the command string that will compare two files. This function will call the diff 
function. This function will not output anything to the screen if there is a difference between the two files. 
This function informs if there is, or is not, a difference between the two files.



