% !TEX root = SystemTemplate.tex


\chapter{Project Overview}
This section provides information regarding the team, project, roles, and such.



\section{Team Members and Roles}
The team members were Colter Assman, Samuel Carroll, and Shaun Greunig.   
Colter Assman was the Scrum Master, Samuel Carroll was the product owner, 
and Shaun Greunig was the Technical Lead for this sprint.


\section{Project  Management Approach}
This program was managed through the Scrum Agile approach to software development.   
The first sprint took place over the course of two week.   The project's main focus points
were compiling source code from tester, log file output, run program with test cases inside 
the program tester, compare the output from the program to expected output, traversing 
a directory to find test cases, and the LaTeX documentation.   The program is owned by the
We Can't Follow Directions team built by request of Dr. Logar, and was controled through 
Trello, and code was distributed through gmail (which will not work for larger teams).



\section{Phase  Overview}
This program started in a gathering information phase, the first thing we had to do as a team 
was generate several questions to ask the customer (Dr. Logar) about the software that she 
wanted.   The next phase was asking if it could be done, as most of the code had been written 
at one point or another for our team, we decided that it was a program that could be written.  
The next phase was breaking the program into smaller milestones, we decided that the program 
would need to compile source code, search for test cases, run compiled code with test case, 
output test case results to a file, compare that output file to an expected output file, and then 
write to a file if the two files match or not, if they do we write the text case then passed to a log 
file, if they don't we write the text case and failed to the log file.   Once we are done traversing the 
directory we write the total number of passed, failed and percentages of each.


\section{Terminology and Acronyms}
GNU - (Recursive Acronym GNU is Not Unix) a operating system often bundled with Linux

Linux - a computer kernel

C++ - a programming language
